\documentclass[11pt,a4paper]{article}

% ─── Packages ────────────────────────────────────────────────────────────────
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{fancyhdr}
\usepackage{titlesec}
\usepackage{tcolorbox}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{forest}
\usepackage{multicol}
\usepackage{tabularx}

% ─── Colors ──────────────────────────────────────────────────────────────────
\definecolor{linkblue}{HTML}{0366D6}
\definecolor{codebg}{HTML}{F6F8FA}
\definecolor{codeframe}{HTML}{D0D7DE}
\definecolor{p0color}{HTML}{D73A49}
\definecolor{p1color}{HTML}{E36209}
\definecolor{p2color}{HTML}{6F42C1}
\definecolor{sectioncolor}{HTML}{24292F}
\definecolor{accentblue}{HTML}{0969DA}

% ─── Hyperref Setup ──────────────────────────────────────────────────────────
\hypersetup{
    colorlinks=true,
    linkcolor=linkblue,
    urlcolor=linkblue,
    citecolor=linkblue,
    pdfauthor={PrivAI 2026 Team},
    pdftitle={DP-ShiftBench: Project Plan},
}

% ─── Code Listing Style ─────────────────────────────────────────────────────
\lstset{
    backgroundcolor=\color{codebg},
    basicstyle=\ttfamily\small,
    breaklines=true,
    frame=single,
    rulecolor=\color{codeframe},
    xleftmargin=1em,
    framexleftmargin=0.5em,
    tabsize=4,
    showstringspaces=false,
}

% ─── Section Formatting ─────────────────────────────────────────────────────
\titleformat{\section}
    {\Large\bfseries\color{sectioncolor}}
    {\thesection}{1em}{}[\vspace{-0.5em}\rule{\textwidth}{0.4pt}]
\titleformat{\subsection}
    {\large\bfseries\color{sectioncolor}}
    {\thesubsection}{1em}{}
\titleformat{\subsubsection}
    {\normalsize\bfseries\color{sectioncolor}}
    {\thesubsubsection}{1em}{}

% ─── Header / Footer ────────────────────────────────────────────────────────
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\small\textcolor{gray}{DP-ShiftBench --- Project Plan}}
\fancyhead[R]{\small\textcolor{gray}{PrivAI 2026}}
\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0.4pt}

% ─── Custom Environments ────────────────────────────────────────────────────
\newtcolorbox{thesisbox}{
    colback=accentblue!5,
    colframe=accentblue!60,
    arc=3pt,
    boxrule=1pt,
    left=10pt, right=10pt, top=8pt, bottom=8pt,
    fontupper=\itshape
}

\newcommand{\priority}[1]{%
    \ifx#1P\def\temparg{#1}\fi
    \textbf{#1}%
}

\newcommand{\ptag}[1]{%
    \ifnum\pdfstrcmp{#1}{P0}=0
        {\textcolor{p0color}{\textbf{P0}}}%
    \else\ifnum\pdfstrcmp{#1}{P1}=0
        {\textcolor{p1color}{\textbf{P1}}}%
    \else
        {\textcolor{p2color}{\textbf{P2}}}%
    \fi\fi
}

% ─── Document ────────────────────────────────────────────────────────────────
\begin{document}

% ─── Title Page ──────────────────────────────────────────────────────────────
\begin{titlepage}
\centering
\vspace*{2cm}

{\Huge\bfseries DP-ShiftBench}\\[0.5cm]
{\LARGE How Distribution Shift Governs\\the Value of Pretraining\\for Private Learning}\\[2cm]

{\Large\textbf{Project Plan}}\\[1cm]

\rule{0.6\textwidth}{0.5pt}\\[1cm]

{\large
\textbf{Course:} PrivAI 2026 (IIT Madras)\\[0.3cm]
\textbf{Instructor:} Krishna Pillutla\\[0.3cm]
\textbf{Problem Statement:} 1.6 --- The Effect of Distribution Shifts\\on Pretraining for Private Learning\\[0.3cm]
\textbf{Project Type:} Original empirical research (with theoretical validation)\\[0.3cm]
\textbf{Target:} Workshop paper at NeurIPS 2026\\(Privacy in ML / Distribution Shift workshops)
}

\vfill

{\large March 2026}

\end{titlepage}

% ─── Table of Contents ───────────────────────────────────────────────────────
\tableofcontents
\newpage

% ══════════════════════════════════════════════════════════════════════════════
\section{Key Dates}
% ══════════════════════════════════════════════════════════════════════════════

\begin{table}[h]
\centering
\begin{tabular}{@{}lll@{}}
\toprule
\textbf{Milestone} & \textbf{Date} & \textbf{Status} \\
\midrule
Project Proposal (2 pages, NeurIPS format) & March 27, 2026 & \texttt{TODO} \\
Mid-Review Report (4 pages) & April 17, 2026 & \texttt{TODO} \\
Project Presentation & April 29 -- May 4, 2026 & \texttt{TODO} \\
Final Report (9 pages) & May 11, 2026 & \texttt{TODO} \\
\bottomrule
\end{tabular}
\caption{Project milestones and deadlines.}
\end{table}

% ══════════════════════════════════════════════════════════════════════════════
\section{Paper Thesis}
% ══════════════════════════════════════════════════════════════════════════════

\begin{thesisbox}
When a model is pretrained on public data and finetuned with DP on private data, how does the distribution shift between these two datasets affect the privacy-utility tradeoff? We build a controlled benchmark (\textbf{DP-ShiftBench}), discover which divergence metrics predict DP degradation, and empirically test whether the interaction between shift and privacy is additive or multiplicative.
\end{thesisbox}

% ══════════════════════════════════════════════════════════════════════════════
\section{Three Core Contributions}
% ══════════════════════════════════════════════════════════════════════════════

% ──────────────────────────────────────────────────────────────────────────────
\subsection{Contribution 1: DP-ShiftBench --- A Controlled Benchmark Suite}
% ──────────────────────────────────────────────────────────────────────────────

A reusable, open-source benchmark where distribution shift is a \textbf{continuous, tunable knob}.

\subsubsection{1A. Image Track: SVHN $\rightarrow$ MNIST}

\begin{small}
\begin{longtable}{@{}p{1.2cm}p{2.5cm}p{2.2cm}p{2.3cm}p{3cm}p{0.6cm}@{}}
\toprule
\textbf{Exp.\ ID} & \textbf{Pretrain Data} & \textbf{Pretrain Method} & \textbf{Finetune Data (DP)} & \textbf{Shift Control Knob} & \textbf{Pri.} \\
\midrule
\endhead
\texttt{IMG-00} & None (random init) & --- & MNIST full & Baseline (no pretrain) & \ptag{P0} \\
\texttt{IMG-01} & SVHN full & Supervised & MNIST full & Full domain gap & \ptag{P0} \\
\texttt{IMG-02} & SVHN digits \{0--4\} & Supervised & MNIST digits \{0--4\} & Matched class subset & \ptag{P0} \\
\texttt{IMG-03} & SVHN digits \{5--9\} & Supervised & MNIST digits \{0--4\} & Mismatched class subset & \ptag{P0} \\
\texttt{IMG-04} & SVHN full & Autoencoder & MNIST full & Task gap & \ptag{P1} \\
\texttt{IMG-05} & SVHN 10\% & Supervised & MNIST full & Data scarcity & \ptag{P1} \\
\texttt{IMG-06} & SVHN 25\% & Supervised & MNIST full & Data scarcity & \ptag{P1} \\
\texttt{IMG-07} & SVHN 50\% & Supervised & MNIST full & Data scarcity & \ptag{P1} \\
\texttt{IMG-08} & CIFAR-10 & Supervised & MNIST full & Larger domain gap & \ptag{P1} \\
\texttt{IMG-09} & SVHN + aug. & Supervised & MNIST full & Style shift & \ptag{P2} \\
\texttt{IMG-10} & FashionMNIST & Supervised & MNIST full & Same format, diff.\ semantics & \ptag{P2} \\
\bottomrule
\end{longtable}
\end{small}

\textbf{Model:} ResNet-18 (or small CNN with ${\sim}500$K parameters for faster iteration).

\paragraph{DP Settings for each experiment:}
\begin{itemize}[nosep]
    \item $\varepsilon \in \{0.5,\ 1.0,\ 2.0,\ 4.0,\ 8.0,\ \infty\ \text{(non-private)}\}$
    \item $\delta = 10^{-5}$
    \item Clipping norm $C \in \{0.1,\ 1.0\}$ (pick best after initial sweep)
    \item Batch size: 256 (with gradient accumulation if needed)
    \item Epochs: 10--20 for finetuning
\end{itemize}

\subsubsection{1B. Language Track: Controlled Markov Chains}

\begin{small}
\begin{longtable}{@{}p{1.2cm}p{2.8cm}p{3.5cm}p{2.5cm}p{0.6cm}@{}}
\toprule
\textbf{Exp.\ ID} & \textbf{Pretrain Distribution} & \textbf{Finetune Distribution (DP)} & \textbf{Shift Control Knob} & \textbf{Pri.} \\
\midrule
\endhead
\texttt{LANG-00} & None & Markov($P_1$) & Baseline & \ptag{P0} \\
\texttt{LANG-01} & Markov($P_1$) & Markov($P_1$) & Zero shift & \ptag{P0} \\
\texttt{LANG-02} & Markov($P_1$) & Markov($0.9 P_1 + 0.1 P_u$) & $\alpha=0.1$ & \ptag{P0} \\
\texttt{LANG-03} & Markov($P_1$) & Markov($0.7 P_1 + 0.3 P_u$) & $\alpha=0.3$ & \ptag{P0} \\
\texttt{LANG-04} & Markov($P_1$) & Markov($0.5 P_1 + 0.5 P_u$) & $\alpha=0.5$ & \ptag{P0} \\
\texttt{LANG-05} & Markov($P_1$) & Markov($0.3 P_1 + 0.7 P_u$) & $\alpha=0.7$ & \ptag{P0} \\
\texttt{LANG-06} & Markov($P_1$) & Markov($P_2$), independent & $\alpha=1.0$ (max shift) & \ptag{P0} \\
\texttt{LANG-07} & Small Transformer & Small Transformer (DP) & Real distribution shift & \ptag{P1} \\
\texttt{LANG-08} & GPT-2 small & GPT-2 small (DP) & Real domain shift & \ptag{P2} \\
\bottomrule
\end{longtable}
\end{small}

\paragraph{Markov Chain Details:}
\begin{itemize}[nosep]
    \item Vocabulary size: 100 tokens
    \item Order: $k=3$ (start), then $k=4$, $k=5$
    \item Transition probabilities $P_1$: randomly generated, then fixed
    \item Shift control: $P_2(\alpha) = (1-\alpha)\,P_1 + \alpha\,P_{\text{uniform}}$
    \item This gives \textbf{exact} KL divergence computation (no estimation needed)
    \item Train a small LSTM or Transformer on sequences from these chains
\end{itemize}

\textbf{Model:} 2-layer LSTM (for Markov) or GPT-2 small (for real text).

\textbf{DP Settings:} Same $\varepsilon$ grid as the image track.

\subsubsection{1C. Benchmark Package Design}

\begin{lstlisting}
dp_shift_bench/
    __init__.py
    datasets/
        image_shifts.py      # SVHN/MNIST/CIFAR shift generators
        markov_chains.py     # Controllable Markov chain distributions
        text_shifts.py       # Real text domain shift loaders
    models/
        image_models.py      # ResNet-18, SmallCNN
        language_models.py   # LSTM, small Transformer
    training/
        dp_trainer.py        # Unified DP-SGD training loop (Opacus)
        standard_trainer.py  # Non-private pretraining loop
    metrics/
        divergences.py       # All divergence measures
        evaluation.py        # Accuracy, perplexity, etc.
    configs/
        image_experiments.yaml
        language_experiments.yaml
    runners/
        run_experiment.py    # Single experiment runner
        run_sweep.py         # Full grid sweep
\end{lstlisting}

% ──────────────────────────────────────────────────────────────────────────────
\subsection{Contribution 2: Divergence-as-Predictor Analysis}
% ──────────────────────────────────────────────────────────────────────────────

For \textbf{every} experiment, compute multiple divergence measures between pretrain and finetune data, then analyze which metric best predicts the DP finetuning performance.

\subsubsection{Divergence Metrics to Compute}

\begin{small}
\begin{longtable}{@{}p{3.2cm}p{3.8cm}p{2.5cm}p{0.6cm}@{}}
\toprule
\textbf{Metric} & \textbf{Implementation} & \textbf{Works For} & \textbf{Pri.} \\
\midrule
\endhead
KL Divergence & Exact (Markov), \texttt{scipy} est.\ (neural) & Language (exact), Images (est.) & \ptag{P0} \\
Reverse KL & Same as above & Both & \ptag{P0} \\
Jensen--Shannon Div. & \texttt{scipy} & Both & \ptag{P0} \\
Total Variation & Exact (Markov), est.\ (neural) & Both & \ptag{P0} \\
MAUVE Score & \texttt{mauve-text} (Pillutla et al.) & Language & \ptag{P0} \\
FID & \texttt{clean-fid} & Images & \ptag{P0} \\
MMD (RBF kernel) & Custom implementation & Both & \ptag{P1} \\
Proxy $\mathcal{A}$-distance & Domain classifier, $2(1-2\epsilon)$ & Both & \ptag{P1} \\
Wasserstein Distance & \texttt{POT} library & Both & \ptag{P1} \\
CKA & Custom (repr.\ similarity) & Both & \ptag{P2} \\
\bottomrule
\end{longtable}
\end{small}

\subsubsection{Analysis Plan}

\begin{enumerate}[nosep]
    \item \textbf{Correlation analysis:} For each metric, compute Pearson/Spearman correlation with DP test accuracy across all experiments.
    \item \textbf{Predictive modeling:} Fit $\text{accuracy}(\varepsilon, d) = f(\varepsilon, d)$ where $d$ is the divergence.
    \item \textbf{Rank the metrics:} Which metric has the highest predictive power?
    \item \textbf{Cross-domain validation:} Does the best predictor on images also work for language?
\end{enumerate}

\subsubsection{Key Plots}

\begin{itemize}[nosep]
    \item \textbf{Scatter plot:} Divergence metric ($x$) vs.\ DP accuracy ($y$), colored by $\varepsilon$ --- one plot per metric
    \item \textbf{Correlation heatmap:} Metrics $\times$ Epsilons, showing $R^2$ values
    \item \textbf{Radar chart:} Comparing predictive power across all metrics
\end{itemize}

% ──────────────────────────────────────────────────────────────────────────────
\subsection{Contribution 3: Additive vs.\ Multiplicative Interaction}
% ──────────────────────────────────────────────────────────────────────────────

\subsubsection{The Competing Hypotheses}

\paragraph{$H_{\text{additive}}$ (current theory --- Bassily et al.\ 2023):}
\begin{equation}
    \text{Error}(\varepsilon, d) = C_1 \cdot \frac{1}{\varepsilon} + C_2 \cdot d + C_3
    \label{eq:additive}
\end{equation}
The DP cost ($1/\varepsilon$) and domain shift cost ($d$) contribute independently.

\paragraph{$H_{\text{multiplicative}}$ (open question):}
\begin{equation}
    \text{Error}(\varepsilon, d) = C_1 \cdot \frac{d}{\varepsilon} + C_2
    \label{eq:multiplicative}
\end{equation}
Distribution shift \textbf{amplifies} the privacy cost --- more shift means you need even more privacy budget.

\paragraph{$H_{\text{threshold}}$ (Setlur et al.\ 2025 ``Goldilocks zone''):}
\begin{equation}
    \text{Error}(\varepsilon, d) =
    \begin{cases}
        C_1/\varepsilon + C_2 \cdot d & \text{if } d < d_{\text{threshold}} \\
        C_1/\varepsilon + C_3 & \text{if } d \geq d_{\text{threshold}}\ \text{(pretrain useless)}
    \end{cases}
    \label{eq:threshold}
\end{equation}
There is a critical shift threshold beyond which public data stops helping.

\subsubsection{Experimental Design}

Run a \textbf{full 2D grid}:
\begin{itemize}[nosep]
    \item $\varepsilon \in \{0.5,\ 1.0,\ 2.0,\ 4.0,\ 8.0,\ \infty\}$
    \item $\text{shift\_level} \in \{0.0,\ 0.1,\ 0.2,\ 0.3,\ 0.5,\ 0.7,\ 1.0\}$ (for Markov: $\alpha$ parameter)
\end{itemize}

This gives a $6 \times 7 = 42$ cell grid. Each cell is repeated 3 times for error bars.\\
\textbf{Total:} 126 runs for language, 126 for images.

\subsubsection{Analysis Plan}

\begin{enumerate}[nosep]
    \item \textbf{3D surface plot:} $\text{accuracy}(\varepsilon, \text{shift})$ --- the ``hero figure''
    \item \textbf{Model fitting:} Fit $H_{\text{additive}}$, $H_{\text{multiplicative}}$, $H_{\text{threshold}}$ to the data. Report AIC/BIC.
    \item \textbf{Phase diagram / heatmap:} 2D plot showing ``gain from pretraining'' $= \text{acc}(\text{pretrained}) - \text{acc}(\text{random\_init})$ as a function of $(\varepsilon, \text{shift})$. Identify the Goldilocks zone boundary.
    \item \textbf{Interaction test:} Two-way ANOVA for significant interaction effect between $\varepsilon$ and shift.
\end{enumerate}

% ══════════════════════════════════════════════════════════════════════════════
\section{Bonus Enhancements (If Time Permits)}
% ══════════════════════════════════════════════════════════════════════════════

\subsection{Enhancement A: Membership Inference Attacks Under Shift}

\begin{description}[nosep]
    \item[Motivation:] Does distribution shift affect \emph{empirical} privacy leakage?
    \item[Method:] Run LiRA or basic shadow-model MIA on DP-finetuned models across shift levels.
    \item[Key question:] Does shift amplify or reduce MIA success rate?
    \item[Priority:] \ptag{P2} \quad \textbf{Effort:} ${\sim}3$ days
\end{description}

\subsection{Enhancement B: Pretraining Data Selection}

\begin{description}[nosep]
    \item[Motivation:] Given a pool of public data, can we \emph{select} a subset that minimizes DP finetuning loss?
    \item[Method:] Use divergence metrics to rank public data subsets, pretrain on top-$k$, evaluate.
    \item[Priority:] \ptag{P2} \quad \textbf{Effort:} ${\sim}2$ days
\end{description}

\subsection{Enhancement C: LoRA vs.\ Full Finetuning Under Shift}

\begin{description}[nosep]
    \item[Motivation:] Does parameter-efficient finetuning (LoRA) behave differently under shift?
    \item[Method:] Repeat key experiments with LoRA finetuning instead of full finetuning.
    \item[Priority:] \ptag{P2} \quad \textbf{Effort:} ${\sim}2$ days
\end{description}

\subsection{Enhancement D: Theoretical Bound Derivation (Stretch)}

\begin{description}[nosep]
    \item[Motivation:] Derive a simple theoretical bound connecting distribution shift to DP finetuning error for convex/linear models.
    \item[Approach:] ~
\end{description}
\begin{itemize}[nosep]
    \item For linear models, the DP-SGD error depends on gradient norm / clipping threshold.
    \item Under distribution shift, the gradient norms change predictably.
    \item Can derive:
    \begin{equation}
        \text{excess\_risk}_{\text{DP}}(\text{shift}) = \mathcal{O}\!\left(\frac{d \cdot C \cdot \sqrt{T} \cdot \sigma}{n}\right) + \mathcal{O}(\text{shift\_distance})
    \end{equation}
    where the $\sigma$ term is the DP noise.
    \item Check if the interaction is additive or multiplicative for this simple case.
\end{itemize}
\textbf{Priority:} \ptag{P2} (but very high impact if achieved) \quad \textbf{Effort:} ${\sim}5$ days

% ══════════════════════════════════════════════════════════════════════════════
\section{Technical Stack}
% ══════════════════════════════════════════════════════════════════════════════

\begin{table}[h]
\centering
\begin{tabularx}{\textwidth}{@{}lll@{}}
\toprule
\textbf{Component} & \textbf{Tool} & \textbf{Notes} \\
\midrule
DP Training & Opacus v1.4+ & PyTorch-based DP-SGD \\
Deep Learning & PyTorch 2.x & Core framework \\
Image Models & torchvision (ResNet-18, CNN) & Pretrained or from scratch \\
Language Models & HuggingFace Transformers & GPT-2 for real text \\
MAUVE Score & \texttt{mauve-text} & Pillutla et al. \\
FID & \texttt{clean-fid} & Image quality metric \\
Optimal Transport & \texttt{POT} & Wasserstein distance \\
Experiment Tracking & Weights \& Biases & Logging all runs \\
Config Management & Hydra + YAML & Reproducible experiments \\
Compute & V100 (16\,GB) & Single GPU sufficient \\
Plotting & matplotlib + seaborn & Publication-quality figures \\
Paper & \LaTeX\ (NeurIPS template) & As required by course \\
\bottomrule
\end{tabularx}
\caption{Technical stack overview.}
\end{table}

% ══════════════════════════════════════════════════════════════════════════════
\section{Project Structure}
% ══════════════════════════════════════════════════════════════════════════════

\begin{lstlisting}
PrivInAI-Project-2026/
|
|-- PROJECT_PLAN.md              # This document
|-- README.md                    # Repo overview
|
|-- dp_shift_bench/              # Main benchmark package
|   |-- __init__.py
|   |-- datasets/
|   |   |-- image_shifts.py      # SVHN/MNIST/CIFAR loaders
|   |   |-- markov_chains.py     # Controllable Markov chains
|   |   |-- text_shifts.py       # Real text domain shift
|   |-- models/
|   |   |-- image_models.py      # ResNet-18, SmallCNN
|   |   |-- language_models.py   # LSTM, small Transformer
|   |-- training/
|   |   |-- dp_trainer.py        # DP-SGD loop (Opacus)
|   |   |-- standard_trainer.py  # Non-private pretraining
|   |   |-- utils.py             # LR schedulers, etc.
|   |-- metrics/
|   |   |-- divergences.py       # All divergence measures
|   |   |-- evaluation.py        # Accuracy, perplexity
|   |-- configs/
|   |   |-- default.yaml
|   |   |-- image_experiments.yaml
|   |   |-- language_experiments.yaml
|   |-- runners/
|       |-- run_single.py        # Run one experiment
|       |-- run_sweep.py         # Full experiment grid
|       |-- run_divergences.py   # Compute divergence metrics
|
|-- experiments/                 # Experiment scripts
|-- analysis/                    # Analysis notebooks
|-- results/                     # Saved results (gitignored)
|-- paper/                       # LaTeX source for reports
|-- tests/                       # Unit tests
|-- requirements.txt
|-- setup.py
\end{lstlisting}

% ══════════════════════════════════════════════════════════════════════════════
\section{Execution Timeline}
% ══════════════════════════════════════════════════════════════════════════════

\textit{Aggressive --- targeting April 17 mid-review with near-complete results.}

\subsection{Week 1: March 22--28 (Proposal Week)}

\textbf{Deadline: Proposal due March 27}

\begin{small}
\begin{longtable}{@{}p{2cm}p{8cm}p{2.5cm}@{}}
\toprule
\textbf{Day} & \textbf{Task} & \textbf{Parallelizable?} \\
\midrule
\endhead
Mar 22--23 & Set up repo, project structure, dependencies & No \\
Mar 22--23 & Read core papers: Li et al., Ganesh et al. & No \\
Mar 23--24 & Implement \texttt{markov\_chains.py} --- data generator & Yes (Agent 1) \\
Mar 23--24 & Implement \texttt{image\_shifts.py} --- SVHN/MNIST loaders & Yes (Agent 2) \\
Mar 23--24 & Implement \texttt{divergences.py} --- KL, JSD, TV & Yes (Agent 3) \\
Mar 24--25 & Implement \texttt{dp\_trainer.py} --- Opacus training loop & No (core) \\
Mar 25--26 & Run first baselines (IMG-00, IMG-01, LANG-00, LANG-01) & Yes \\
Mar 26--27 & \textbf{Write 2-page proposal} & No \\
Mar 27 & \textbf{SUBMIT PROPOSAL} & --- \\
\bottomrule
\end{longtable}
\end{small}

\subsection{Week 2: March 29 -- April 4 (Core Experiments)}

\begin{small}
\begin{longtable}{@{}p{2cm}p{7cm}p{2.5cm}p{1.5cm}@{}}
\toprule
\textbf{Day} & \textbf{Task} & \textbf{Parallel?} & \textbf{Est.\ Time} \\
\midrule
\endhead
Mar 29--30 & Run full image grid (IMG-00 to IMG-08) & Yes (Agent 1) & ${\sim}8$h GPU \\
Mar 29--30 & Run full Markov language grid (LANG-00 to LANG-06) & Yes (Agent 2) & ${\sim}2$h GPU \\
Mar 29--30 & Implement remaining divergences (MAUVE, FID, MMD, Wasserstein) & Yes (Agent 3) & --- \\
Mar 31 -- Apr 1 & Compute ALL divergence metrics for ALL dataset pairs & Yes & ${\sim}4$h \\
Apr 1--2 & Run 2D grid ($\varepsilon \times$ shift) --- language & Yes (Agent 1) & ${\sim}6$h \\
Apr 1--2 & Run 2D grid ($\varepsilon \times$ shift) --- images & Yes (Agent 2) & ${\sim}12$h \\
Apr 2--3 & Implement proxy $\mathcal{H}$-divergence (domain classifier) & Yes (Agent 3) & --- \\
Apr 3--4 & Run P1 experiments (IMG-04--07, LANG-07) & Yes & ${\sim}8$h \\
\bottomrule
\end{longtable}
\end{small}

\subsection{Week 3: April 5--11 (Analysis \& Extra Experiments)}

\begin{small}
\begin{longtable}{@{}p{2cm}p{8.5cm}p{2.5cm}@{}}
\toprule
\textbf{Day} & \textbf{Task} & \textbf{Parallel?} \\
\midrule
\endhead
Apr 5--6 & Contribution 2 analysis: correlation, predictive modeling & Yes (Agent 1) \\
Apr 5--6 & Contribution 3 analysis: model fitting, ANOVA & Yes (Agent 2) \\
Apr 5--6 & Generate ALL hero figures & Yes (Agent 3) \\
Apr 7--8 & Enhancement A (MIA under shift) --- if time permits & Optional \\
Apr 7--8 & Enhancement C (LoRA comparison) --- if time permits & Optional \\
Apr 9--10 & Run failed/missing experiments, collect final results & --- \\
Apr 10--11 & Create results summary tables & --- \\
\bottomrule
\end{longtable}
\end{small}

\subsection{Week 4: April 12--17 (Mid-Review Report)}

\begin{small}
\begin{longtable}{@{}p{2cm}p{10cm}@{}}
\toprule
\textbf{Day} & \textbf{Task} \\
\midrule
\endhead
Apr 12--13 & Write mid-review Sections 1--2 (intro, literature survey with math) \\
Apr 13--14 & Write mid-review Section 3 (experimental setup, benchmark design) \\
Apr 14--15 & Write mid-review Section 4 (results so far) \\
Apr 15--16 & Create all figures and tables for mid-review \\
Apr 16--17 & Polish, proofread, finalize \\
Apr 17 & \textbf{SUBMIT MID-REVIEW} \\
\bottomrule
\end{longtable}
\end{small}

\subsection{Weeks 5--6: April 18 -- May 4 (Presentation + Remaining Work)}

\begin{small}
\begin{longtable}{@{}p{7cm}p{5cm}@{}}
\toprule
\textbf{Task} & \textbf{Timeline} \\
\midrule
\endhead
Enhancement experiments (MIA, LoRA, data selection) & Apr 18--22 \\
Package \texttt{dp\_shift\_bench} for release & Apr 22--25 \\
Prepare presentation slides & Apr 25--28 \\
\textbf{PRESENT} & Apr 29 -- May 4 \\
\bottomrule
\end{longtable}
\end{small}

\subsection{Week 7: May 5--11 (Final Report)}

\begin{small}
\begin{longtable}{@{}p{7cm}p{5cm}@{}}
\toprule
\textbf{Task} & \textbf{Timeline} \\
\midrule
\endhead
Write full 9-page report & May 5--9 \\
Final figures, proofreading & May 9--10 \\
\textbf{SUBMIT FINAL REPORT} & May 11 \\
\bottomrule
\end{longtable}
\end{small}

% ══════════════════════════════════════════════════════════════════════════════
\section{Key References}
% ══════════════════════════════════════════════════════════════════════════════

\subsection{Core References (from course document)}

\begin{small}
\begin{longtable}{@{}p{0.6cm}p{3.5cm}p{5.5cm}p{0.7cm}p{2.5cm}@{}}
\toprule
\textbf{Ref} & \textbf{Authors} & \textbf{Title} & \textbf{Year} & \textbf{Relevance} \\
\midrule
\endhead
{[21]} & Li, Tramer, Liang, Hashimoto & Large language models can be strong differentially private learners & 2022 & Why pretraining helps DP \\
{[22]} & Ganesh, Haghifam, Nasr, Oh, Steinke, Thakkar, Thakurta, Wang & Why is public pretraining necessary for private model training? & 2023 & Two-phase hypothesis \\
{[10]} & Pillutla, Swayamdipta, Zellers, et al. & MAUVE: Measuring the Gap Between Neural Text and Human Text & 2021 & Distribution gap measurement \\
{[11]} & Pillutla, Liu, Thickstun, et al. & MAUVE Scores for Generative Models: Theory and Practice & 2023 & Extended MAUVE theory \\
{[23]} & Netzer et al. & Reading digits in natural images with unsupervised feature learning (SVHN) & 2011 & SVHN dataset \\
{[24]} & Sakarvadia et al. & Mitigating memorization in language models & 2025 & Language memorization \\
\bottomrule
\end{longtable}
\end{small}

\subsection{Additional Key References (from literature search)}

\begin{small}
\begin{longtable}{@{}p{3.2cm}p{5.5cm}p{0.7cm}p{3cm}@{}}
\toprule
\textbf{Authors} & \textbf{Title} & \textbf{Year} & \textbf{Relevance} \\
\midrule
\endhead
Setlur, Thaker, Ullman & Lower Bounds for Public-Private Learning under Distribution Shift & 2025 & Goldilocks zone theory \\
Bassily, Cortes, Mao, Mohri & Differentially Private Domain Adaptation with Theoretical Guarantees & 2023 & Additive bound (we test this) \\
Ben-David, Blitzer, Crammer, et al. & A theory of learning from different domains & 2010 & Domain adaptation theory \\
Auddy, Cai, Chakraborty & Minimax and Adaptive Transfer Learning under Distributed DP & 2025 & Minimax rates for private transfer \\
Dong, Roth, Su & Gaussian Differential Privacy & 2022 & GDP framework \\
Tobaben et al. & On the Efficacy of DP Few-shot Image Classification & 2023 & DP with pretrained features \\
De, Berrada, Hayes, Smith, Balle & Unlocking High-Accuracy DP Image Classification through Scale & 2022 & Scaling + pretraining for DP \\
Li, Guo, Li, Fan, Hu, Liu & PrivLM-Bench & 2024 & Existing DP benchmark (no shift) \\
Yichuan, Kotevska, Reshniak & Assessing MIA under Distribution Shifts & 2024 & MIA + shift \\
\bottomrule
\end{longtable}
\end{small}

% ══════════════════════════════════════════════════════════════════════════════
\section{Risk Register}
% ══════════════════════════════════════════════════════════════════════════════

\begin{table}[h]
\centering
\begin{tabularx}{\textwidth}{@{}Xllp{4.5cm}@{}}
\toprule
\textbf{Risk} & \textbf{Likelihood} & \textbf{Impact} & \textbf{Mitigation} \\
\midrule
GPU time insufficient for full grid & Low & High & Prioritize P0 experiments; reduce grid \\
Markov chain results too ``toy'' & Medium & Medium & Include real text experiments (LANG-07/08) \\
No clear winner among divergence metrics & Medium & Low & Valid negative result \\
Additive vs.\ multiplicative inconclusive & Medium & Medium & Report fitted models; let data speak \\
Opacus bugs / compatibility issues & Low & High & Pin versions; test early \\
Proposal too ambitious for reviewers & Low & Low & Clearly mark P0/P1/P2 priorities \\
\bottomrule
\end{tabularx}
\caption{Risk register with mitigation strategies.}
\end{table}

% ══════════════════════════════════════════════════════════════════════════════
\section{Success Criteria}
% ══════════════════════════════════════════════════════════════════════════════

\subsection{Minimum Viable Paper (Course Project)}

\begin{itemize}[nosep]
    \item[$\square$] DP-ShiftBench with image track (P0 experiments) working
    \item[$\square$] DP-ShiftBench with language Markov track (P0 experiments) working
    \item[$\square$] At least 4 divergence metrics computed and correlated with DP accuracy
    \item[$\square$] 2D grid ($\varepsilon \times$ shift) for either images or language
    \item[$\square$] Phase diagram / hero figure
    \item[$\square$] Clear narrative about which metric predicts DP degradation
\end{itemize}

\subsection{Full Paper (Workshop Submission)}

All of the above, \textbf{plus}:
\begin{itemize}[nosep]
    \item[$\square$] Both image AND language tracks complete
    \item[$\square$] All 6+ divergence metrics computed and compared
    \item[$\square$] Formal additive vs.\ multiplicative hypothesis test
    \item[$\square$] Cross-domain validation (best predictor on images also works for language?)
    \item[$\square$] Open-source benchmark package released
    \item[$\square$] At least one enhancement (MIA, LoRA, or data selection)
\end{itemize}

\subsection{Stretch Goals (Full Conference Paper)}

\begin{itemize}[nosep]
    \item[$\square$] Theoretical bound derivation for linear models
    \item[$\square$] Enhancement D complete
    \item[$\square$] Extended to more realistic datasets (CIFAR-100, real NLP)
    \item[$\square$] Temporal shift experiments
\end{itemize}

\end{document}
